\documentclass{article}
\usepackage{url}
\usepackage{fancysection}
\colorsections{200}
\title{Examples of \hevea{} usage}

\begin{document}\maketitle

\section*{Some examples on the web}
\begin{tocenv}
\item Courses
\begin{tocenv}
\item The on-line
``\ahref{http://www.enseignement.polytechnique.fr/profs/informatique/Luc.Maranget/compil/poly/}{\emph{polycopi\'e}}''
of my compilation course at \'Ecole polytechnique.
Another
``\ahref{http://www.enseignement.polytechnique.fr/profs/informatique/Luc.Maranget/421/poly/}{\emph{polycopi\'e}}'' of mine.
\item Another on-line
``\ahref{http://www.enseignement.polytechnique.fr/informatique/ARCHIVES/IF/poly/index.html}{\emph{polycopi\'e}}''
from \'Ecole polytechnique.
\item \ahref{http://www.grappa.univ-lille3.fr/polys/reseaux-2004/index.html}{Another course}, from Universit\'e de Lille~III.
\end{tocenv}
\item Manuals and tutorials.
\begin{tocenv}
\item The on-line manual of \ahref{\url|http://www.di.ens.fr/~pouzet/lucid-synchrone/manual_html/index.html|}{Lucid Synchrone}.
\item The on-line
\ahref{http://caml.inria.fr/pub/docs/manual-ocaml/index.html}{Objective
Caml} manual.
\item The on-line
\ahref{http://www.lifl.fr/\home{boulet}/softs/mldoc/index.html}{MlDoc}
manual. MlDoc is a literate programming tool.
\item The on-line
\ahref{http://omake.metaprl.org/omake.html}{OMake} manual.
\end{tocenv}
\end{tocenv}


\section*{Examples from the distribution}
Source for these examples is included in the distribution in
sub-directory \texttt{examples}.
\begin{itemize}
\item The \ahrefurl{Makefile}

\item A simple article,  source is \ahrefurl{a.tex}.
You can compare \LaTeX{} output (\ahrefurl{a.dvi}) and \hevea{} output~\ahrefurl{a.html}. The \html{} output is
generated with the french option set:
\begin{verbatim}
# hevea a.tex
\end{verbatim}
While the text output generated with:
\begin{verbatim}
# hevea -text a.tex
\end{verbatim}

\item The test suite: \ahrefurl{suite.tex}
(\hevea{} style file \ahrefurl{suite-macros.hva}, \LaTeX{} style file
\ahrefurl{suite-macros.sty})
and \ahrefurl{suite.html} (see
also \ahrefurl{suite.dvi} and \ahrefurl{suite.txt}).

\item A complete article, cut into pieces , with images (source is
\ahrefurl{pat.tex}, output is \ahrefurl{pat.dvi}, 
\ahrefurl{pat.html} and \ahrefurl{pat.txt}). To yield this result, \verb+gpic+ is first
applied to \verb+pat.tex+, yielding \verb+tmp.tex+; \LaTeX\ and
\texttt{bibtex} are then used to produce the appropriate \verb+tmp.aux+ and
\verb+tmp.bbl+ files; finally \hevea{}, \hacha{} and \texttt{imagen}
are run as follows:
\begin{verbatim}
# hevea pat.hva -e pat.def tmp.tex
# hacha -o pat.html tmp.html
# imagen tmp
\end{verbatim}
Notice that the \LaTeX{} style file \ahrefurl{pat.def} is not loaded and
that a simplified \ahrefurl{pat.hva} is loaded.

Using option ``\texttt{-fix}'', \texttt{imagen} does not need to be
run explicitely~:
\begin{verbatim}
# hevea -fix pat.hva -e pat.def tmp.tex
# hacha -o pat.html tmp.html
\end{verbatim}

This example also serves as a test of \hacha{} advanced features,
direct access to the article \ahref{conclusion.html}{conclusion}
and \ahref{benchmarks.html}{performance figures}.

\item How to use the \verb+latexonly+ and \verb+toimage+ environments
inside other environments.
Source files are \ahrefurl{env.hva} and
\ahrefurl{env.tex}), output file is \ahrefurl{env.html}.
\texttt{gpic}, \hevea{} and \texttt{imagen}
are run as follows:
\begin{verbatim}
# gpic -t < env.tex > tenv.tex
# hevea env.hva tenv.tex -o env.html
# imagen env
\end{verbatim}

\item The ``\emph{Smile!}'' example, from the manual.
Files are \ahrefurl{smile.hva}, \ahrefurl{smile.tex} and
\ahrefurl{smile.html}, command sequence is~:
\begin{verbatim}
# gpic -t < smile.tex > tsmile.tex
# hevea smile.hva tsmile.tex -o smile.html
# imagen smile
\end{verbatim}

\item A few amstex primitives, \ahrefurl{amstex.tex},
\ahrefurl{amstex.dvi}, \ahrefurl{amstex.html} and \ahrefurl{amstex.txt}.
\hevea{} is invoked as:
\begin{verbatim}
# hevea [-text] amstex.tex
\end{verbatim}

\item The \texttt{graphics} package, \ahrefurl{graphics.tex}
and \ahrefurl{graphics.html}.
\hevea{} is invoked as:
\begin{verbatim}
# hevea graphics.tex
# imagen graphics
\end{verbatim} 

\item A lot of symbols, \ahrefurl{sym.html}.
Almost all the symbols provided by default and by packages
\texttt{latexsym},
\texttt{textcomp},
\texttt{amssymb} and \texttt{amsmath}.

\item \ahref{boxes.html}{Boxes}, boxes (and lengths).

\item \ahref{test/index.html}{More tests}: systematic tests of some of \hevea{} features.
\end{itemize}
\end{document}
